Miniproject - Analytic Number Theory

### 2021-12-08 Analytic number theory/submission.tex
Added result from literature search to ANT

First, we will bound the value of the partial sums of the Dirichlet series for $0 < \Re(s) \leq 1$.

@@

    \label{prop:character_partsums_bounded}
    Let $\chi \neq \chi_0$ be a Dirichlet character.
    Then for $\Re(s) > 0$ have
        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq q + \frac {q|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
    and in particular, this does not depend on $X$.

@@

    Using partial summation yields
        \sum_{1 \leq n \leq X} \chi(n) n^{-s} =& \sum_{1 - \epsilon < n \leq X} \chi(n) n^{-s} \\
        =& \underbrace{A(1 - \epsilon)}_{= 0} (1 - \epsilon)^{-s} - A(X) X^{-s} + s\int_{1 - \epsilon}^X A(t) t^{-(s + 1)} dt \\
        =& -A(X) X^{-s} + s\int_1^X A(t) t^{-(s + 1)} dt
        \Bigl| \sum_{1 \leq n \leq X} \chi(n) n^{-s} \Bigr| \leq& \ |A(X) X^{-s}| + |s| \int_1^X |A(t) t^{-(s + 1)}| dt \\
        \leq& \ q X^{-\Re(s)} + |s| \int_1^X q t^{-\Re(s) - 1} dt \\
        =& \ q X^{-\Re(s)} + q|s| \left( \frac 1 {\Re(s)} - \frac 1 {X^{\Re(s)}\Re(s)} \right) \\
        \leq& \ q + q \frac {|s|} {\Re(s)} = O\left( \frac {q|s|} {\Re(s)} \right)
    for $\Re(s) > 0$.

@@

    Similar to the proof of Lemma~\ref{prop:character_partsums_bounded}, partial summation yields

@@

        \sum_{n \geq 1} \chi(n) n^{-s} = s \int_1^\infty A(t) t^{-(s + 1)} dt

@@

    By Lemma~\ref{prop:character_partsums_bounded}, this is bounded and hence well-defined and finite for $\Re(s) > 0$.

>>>>

First, we will bound the value of the partial sums of a Dirichlet character.

@@

This bound is already strong enough to show the analytic continuation of $L(s, \chi)$ to $\Re(s) > 0$.
However, the best known results are significantly stronger than that.
\begin{proposition}[Pólya–Vinogradov inequality]
    Then for all $n \in \N$, have $|A(n)| = O(\sqrt{q}\log(q))$.

@@

    See \cite[Ch. 23]{davenport}.

@@

    Using partial summation, we find for some $0 < \epsilon < 1$ that

@@

        \sum_{n \geq 1} \chi(n) n^{-s} =& A(1 - \epsilon) (1 - \epsilon)^{-s} - (-s) \int_{1 - \epsilon}^\infty A(t) t^{-(s + 1)} dt \\
        =& s \int_1^\infty A(t) t^{-(s + 1)} dt

@@
